Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-09 lids/twittersearchwrap/paper/paper.tex

\usepackage{fullpage}
\usepackage{setspace}
\usepackage{url}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{latexsym}

@@

\onehalfspacing

@@

\begin{abstract}
To facilitate understanding the meaning of a hash tag in the context of Twitter, we have developed a system which annotates hash tags based on Twitter search results with encyclopedia entities that best describe the hash tag, thus offering means of quickly grasping the meaning of the hash tag and at the same time providing starting points for further exploration of the hash tags' context. In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e. when executing the same search at different times, the same entities are returned.
\end{abstract}

@@

\myremark{todo}{warum kein direktes Mapping auf dbpedia-Entitäten?}

@@

On Twitter it is possible to search for messages containing a specific term or hash tag. This search returns a fixed number of most recent messages containing the search term. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single Twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.

@@

\myremark{todo}{ergänzen: abkürzungen, verschmelzen von Wörtern}

@@

The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).

@@

  \myremark{todo}{ausführen}
In our example, the message contains a link to
\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
text found at the link gives us the following text: ''\texttt{Karlsruhe, where
paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''

@@

\myremark{todo}{Wo ist das System zugreifbar?}

@@

@@

Topics trending worldwide and in Germany on Twitter retrieved on February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

\begin{table}[ht*]
\centering
\begin{tabular}{ |l|l| }
\hline
\textsc{Trending Topic} & \textsc{Location}  \\
\hline
\#goodlucknickj & Worldwide \\
\#smalljoys & Worldwide \\
\#thingsthedevilinvented & Worldwide \\
Adam Wainwright & Worldwide \\
CatchPetrovaFire & Worldwide \\
Gadafi & Worldwide \\
Libia & Worldwide \\
Precious Minaj & Worldwide \\
Tommy John & Worldwide \\
\hline
\#gaddafi & Germany \\
\#guttenberg & Germany \\
\#libya & Germany \\
Doktorarbeit & Germany \\
Gef\"{u}hl & Germany \\
Lion & Germany \\
MBP & Germany \\
Thunderbolt & Germany \\
Vorratsdatenspeicherung & Germany \\
\hline
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

\myremark{todo}{Deutsche Themen nicht ausgewertet wegen Sprachproblem}

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries and saved the returned data. Two methods for this data acquisition
were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item {\bf Temporal Sliding Window}\newline The query is executed and the n
most recent results are retrieved every t minutes. The Temporal Sliding Window
method may lead to duplicate messages in the retrieved documents, but needs to
handle much less data and allows for an analysis over larger time frames.
\item {\bf k-item Sliding Window}\newline  The k-item Sliding Window methods
retrieves all messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\myremark{todo}{Nicht genau machbar wegen Zeitpunkt, wann Lookup gemacht werden soll, nicht bekannt}
\end{itemize}
\end{definition}

We considered the trending topics on Twitter a good set of input queries for
our evaluation approach. Trending topics often cover a variety of recently
talked about topics which due to its recent nature may be of high interest for
further processing. Using the retrieved trending topics given in Table
\ref{tbl:terms} as input queries for the evaluation, the set of queries was executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame starting from the moment the topics were identified as trending topics. We chose the Temporal Sliding Window method for data acquisition because of the expected data volume generated by trending topics as search terms and the long term nature of our evaluation approach. We have then evaluated the results
with respect to several measures:

>>>>

%\usepackage{fullpage}
\usepackage{setspace}
\usepackage{url}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{latexsym}

@@

%\onehalfspacing

@@

\begin{abstract}
To facilitate understanding the meaning of a hash tag in the context of Twitter, we have developed a system which annotates hash tags based on Twitter search results with encyclopedia entities that best describe the hash tag, thus offering means of quickly grasping the meaning of the hash tag and at the same time providing starting points for further exploration of the hash tags' context. In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e. when executing the same search at different times, the same encyclopedia entities are returned.
\end{abstract}

@@

@@

On Twitter it is possible to search for messages containing a specific hash tag. This search returns a fixed number of most recent messages containing the tag. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single Twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.

@@

@@

The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}). Note however that a direct mapping of hash tags to entities is not possible in many cases: e.g. there is no entity in dbpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.

@@

In our example, the message contains a link to
\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
text found at the link gives us the following text: ''\texttt{Karlsruhe, where
paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''

@@

@@

We have evaluated our approach to assess whether the entities which are found as related to a specific hash tag are useful and stable over time.

@@

We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}. Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.

\begin{table}[ht*]
\centering
\begin{tabular}{ l }
Trending Topics Worldwide  \\
\hline
\#goodlucknickj  \\
\#smalljoys \\
\#thingsthedevilinvented \\
Adam Wainwright  \\
CatchPetrovaFire \\
Gadafi  \\
Libia \\
Precious Minaj \\
Tommy John  \\
\end{tabular}
\begin{tabular}{l}
Trending Topics Germany \\
\hline
\#gaddafi \\
\#guttenberg  \\
\#libya  \\
Doktorarbeit \\
Gef\"{u}hl  \\
Lion  \\
MBP \\
Thunderbolt \\
Vorratsdatenspeicherung \\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

The second query set consists of hash tags that are frequently used on Twitter. To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.

\begin{table}[ht*]
\centering
\begin{tabular}{ l|l }
Hashtag & Count  \\
\hline
ff &     460 \\
np &     172 \\
nowplaying &     144 \\
winning &     134 \\
fb &     105 \\
rt &      83 \\
mentionke &      61 \\
blackpeoplemovies &      57 \\
tigerblood &      56 \\
thataintwinning &      53 \\
fail &      53 \\
teamfollowback &      52 \\
iftwitterwashighschool &      51 \\
bieberfact &      51 \\
news &      46 \\
jobs &      45 \\
libya &      44 \\
followmejp &      44 \\
partiu &      41 \\
sougofollow &      39 \\
damnitstrue &      39 \\
tilltheworldends &      37 \\
soalcinta &      35 \\
nicovideo &      35 \\
quran &      33 
\end{tabular}
\begin{tabular}{ l|l }
Hashtag & Count  \\
\hline
nw &      32 \\
quote &      31 \\
shoutout &      30 \\
jfb &      30 \\
carnaval &      27 \\
tfb &      26 \\
followme &      26 \\
followfriday &      25 \\
follow &      24 \\
egypt &      23 \\
retweet &      22 \\
fact &      22 \\
win &      20 \\
tweetmyjobs &      20 \\
music &      20 \\
in &      20 \\
imagine &      20 \\
nowwatching &      19 \\
cumannanyaindonesia &      19 \\
twexit &      18 \\
lcv &      18 \\
fui &      18 \\
bot &      18 \\
nemuritsuzuketeshinu &      17 \\
fato &      17 \\
\end{tabular}
\caption{Popular hashtags sampled during a three-day period.}\label{tbl:hashtags}
\end{table}

The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries and analysed the returned data.

In principle, two methods for data acquisition were identified: \begin{definition}[Data Acquisition Methods]
\begin{itemize}
\item {\bf Temporal Sliding Window}\newline The query is executed and the n
most recent results are retrieved every t minutes. The Temporal Sliding Window
method may lead to duplicate messages in the retrieved documents, but needs to
handle much less data and allows for an analysis over larger time frames.
\item {\bf $k$-item Sliding Window}\newline  The k-item Sliding Window methods
retrieves all messages that match the query exactly one time. Each time k new messages are
available matching the given query a document containing those k messages
is retrieved. This method can lead to high data volume and needs constant
monitoring of recently posted messages matching the search term.
\end{itemize}
\end{definition}

The disadvantage of the first method is that it is neither possible to guarantee that all messages matching the search are collected, nor is it possible to avoid overlaps between the search results. However, while the second method seems to overcome these problems, it does not: Using the $k$-item sliding window method, it is not clear when the next search result should be fetched: even when frequently querying for new messages, if updates are frequent it is likely to lack messages in the result set.

For both data set queries were executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame. Data for the trending topics was collected on 2011-02-24, for the frequent hash tags data was collected on 2011-03-07.

@@

For analysing the collected data, several measures were defined:
